### 2011-06-14 standing-patches-paper.tex
/* Paper */ removed missing figure
/* Paper */ added some figures...

\subsection{Results}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\textwidth]{proportion-by-sigma.eps}
\caption{ %
{\bf Mean proportion of patches arising from standing variation.} The paramters given are for the sickle-cell example.  XXX say more.
}
\label{fig:cartoon}
\end{center}

\end{figure}

@@

\subsection{ss:discretedemes}

@@

\subsection{Patchy Results} 
\label{ss:discreteresults}

@@

 \begin{figure}[ht]
 \begin{center}
 %\includegraphics{discrete-by-mutrate.eps}
 %\includegraphics{discrete-by-migrprob.eps}
 \includegraphics{discrete-by-ratio.eps}
 \filenote{discrete-by-ratio.eps}
 \caption{ %
 The mean number of types and the mean number of demes occupied by a sampled type, in a discrete model with 20 demes,
 plotted as a function of the ratio of migration to mutation probabilities.
 Note the log scale on the horizontal axis.
 \label{fig:discbyratio}
 }
 \end{center}
 \end{figure}

>>>>

\subsection{Standing Variation -- Results}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\textwidth]{charlen-by-sd-limit}
\caption{ %
{\bf Characteristic length,} as a function of selective disadvantage, compared to the corresponding quantity without standing variation (e.g.\ from \cite{ralphcoop2010}) and to the quantity only considering standing variants (e.g.\ $\sqrt{\lambda_0}$).
}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\textwidth]{proportion-by-sigma.eps}
\caption{ %
{\bf Mean proportion of patches arising from standing variation.} The paramters given are for the sickle-cell example.  XXX say more.
}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\textwidth]{proportion-contour.png}
\caption{ %
{\bf Mean proportion of area occupied by standing variants,} as a function of dispersal distance $\sigma$ and selective disadvantage $s_d$.  XXX at what parameters. XXX
}
\end{center}
\end{figure}

@@

\subsection{Discrete populations}
\label{ss:discretedemes}

@@

\subsection{Patchy Selection -- Results} 
\label{ss:discreteresults}

@@

 \begin{figure}[ht]
 \begin{center}
 %\includegraphics{discrete-by-mutrate.eps}
 %\includegraphics{discrete-by-migrprob.eps}
 \includegraphics{discrete-by-ratio}
 \caption{ %
 The mean number of types and the mean number of demes occupied by a sampled type, in a discrete model with 20 demes,
 plotted as a function of the ratio of migration to mutation probabilities.
 Note the log scale on the horizontal axis.
 \label{fig:discbyratio}
 }
 \end{center}
 \end{figure}
